\documentclass[letterpaper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage[margin=16mm]{geometry}
\usepackage{nopageno}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage{titlesec}

\usepackage{ifxetex,ifluatex}

\linespread{1}
\setcounter{secnumdepth}{0}

\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines

\setlist{leftmargin=3.5mm}


\providecommand{\tightlist}
  {\setlength{\itemsep}{4pt}\setlength{\parskip}{0pt}}

% Skills definition list type
\newlist{skills}{description}{1}
\setlist[skills]{leftmargin=11em,style=nextline}

% For the section heading allow runin so we can align text to the right
\titleformat{\section}[runin]
  {\normalfont\Large\bfseries}
  {}{0pt}{}

\titleformat{\subsubsection}[runin]
  {\normalfont\bfseries}
  {}{0pt}{}

% \usepackage{resume}
\usepackage[
bookmarks=true,
unicode=true,
pdfauthor={Caleb Jasik},
pdftitle={Caleb Jasik's Resume}]{hyperref}

\begin{document}

    \section{\Huge Caleb Jasik}\label{sec:hugecaleb-jasik}

    \hfill 104 N Houston St. \#1742 College Station, TX 77841

    \hfill \href{mailto:calebjasik@jasik.xyz}{calebjasik@jasik.xyz} ---
    \href{https://jasik.xyz}{https://www.jasik.xyz}

    \subsection{Qualifications}\label{subsec:qualifications}

    Summa Cum Laude - CyFair High School 2016

    \href{https://www.coursera.org/account/accomplishments/verify/GZEYJ5VA2YGH}{Technical Support Fundamentals} - Coursera July 2019

    \begin{skills}
        \item[Programming]
        HTML, CSS, Javascript, Java, C++, C, Rust, Python, and Haskell. Markdown and LaTeX.

        All self-taught, with directed learning for Java, C++, and C\@.
        \item[Machine Learning]
        Basic Understanding of: Linear regression, K-means, CNNs, Clustering algorithms, RNNs.
        \item[Embedded Systems]
        Basic Understanding of: Basic CLC design, Arduino and TI embedded systems
        \item[Other Interests]
        User Experience design, Usability, Accessibility
    \end{skills}


    \subsection{Experience}\label{subsec:experience}

    \subsubsection{College Music}
    \hfill Freelance Web Developer --- \emph{July 2020 - October 2020}

    Worked on a dynamic, user accessible and responsive standalone site for the lofi streaming company College Music. I've learned a lot about client-side javascript and API's with this one.

    \subsubsection{G-Power}
    \hfill Freelance Web Developer --- \emph{March 2020 - October 2020}

    Originally a Wordpress site serving 6kb on the homepage, it soon will serve only 308kb and is fully responsive and a main goal is for it to be accessible for every customer of G-Power.

    \subsubsection{Chicken Oil Company}
    \hfill Cashier and Cook --- \emph{May 2019 - May 2020}

    Worked quickly in a team of 2-5 team members to deliver quality meals to customers in a timely manner.

    \subsubsection{TAMU Collegiate Content Creatives}
    \hfill One-Off Project for College Club --- \emph{September 2018}

    Created a continuously-delivered static landing page for my college club.

    \subsubsection{Duddley's Draw}
    \hfill Bouncer and Cook --- \emph{August 2018 - April 2019}

    Verified age and sobriety of customers at door. Worked quickly, under pressure to prepare a variety of delicious food-stuffs.


    \subsubsection{Chick-fil-a}
    \hfill Cashier and Cook --- \emph{April 2015 - January 2019}

    Flexibly worked any position in the restaurant required quickly, with a specific attention to detail and ability to pull long shifts of continuous work.

    \subsubsection{Forest Glen Springs Camp / Camp Wilderness Ridge}
    \hfill Program Staff and Camp Counselor 
    
    \hfill \emph{May 2012 - September 2017}

    \begin{itemize}
        \tightlist{}
        \item
        Worked in a team promoting safety and fun on the low ropes Challenge Course.
        Belayed campers on the climbing wall and traversing bridge, transferred campers from the climbing elements to the zip-lines and encouraged them to face their fears and have fun.
        \item
        Facilitated archery and marksmanship, encouraging novice marksmen and markswomen, and teaching best practices for safety, accuracy, and excitement.
        \item
        Organized the water front activities: Stand-up paddle boards, canoes, The Blob, and kayaks, with a safety and fun oriented attitude.
        \item
        Organized games and team building exercises to grow relationships, teach the campers, and have fun.
        \item
        Led the campers through low-ropes team building exercises.
        \item
        Worked through the daily bible study and nightly talk with the campers.
        \item
        Encouraged and assisted campers in memorizing the daily bible verses.
    \end{itemize}

    \subsubsection{Texas A\&M University, College Station, Texas}
    \hfill Student, Incomplete --- \emph{January 2017 - December 2019}

    Completed 25 hours towards a BS in Computer Science, and then 25 hours towards a BS in Electrical Systems Engineering Technology. Didn't take. I intend to complete my education in computer science, though not at Texas A\&M.
\end{document}