\documentclass[letterpaper,10pt]{article}

\usepackage{resume}
\usepackage[pdftex,
bookmarks=true,
unicode=true,
pdfauthor={Caleb Jasik},
pdftitle={Caleb Jasik's Resume}]{hyperref}

\begin{document}

    \section{\Huge Caleb Jasik}\label{sec:hugecaleb-jasik}

    \hfill Wellborn Rd. Bryan, TX 77801

    \hfill \href{mailto:jasikpark@tamu.edu}{jasikpark@tamu.edu} ---
    \href{tel:2816149841}{(281) 614--9841}

    \hfill \href{https://github.com/jasikpark}{https://github.com/jasikpark}

    \hfill \href{https://jasik.xyz}{https://www.jasik.xyz}

    \subsection{Qualifications}\label{subsec:qualifications}

    Summa Cum Laude - CyFair High School 2016

    BS - Electrical Systems Engineering Technology 2021

    Texas A\&M University, College Station, Texas


    \subsection{Skills}\label{subsec:skills}

    \begin{skills}
        \item[Soft Skills]
        Good Problem-Solver, Communicates Well, Attention to Detail, Quick Learner
        \item[Programming]
        Javascript, Java, C++, C, Rust, Python, and Haskell. Markdown and LaTeX.

        All self-taught, with directed learning for Java, C++, and C\@.
        \item[Machine Learning]
        Linear regression, K-means, CNNs, Clustering algorithms, RNNs.
        \item[Embedded Systems]
        Basic CLC design, Arduino and TI embedded systems
        \item[Other Interests]
        User Experience design
        \item[Websites]
        Principal developer for \href{https://www.tamuccc.com}{https://www.tamuccc.com} for the TAMU Collegiate Content Creatives
        \item[Software]
        Microsoft Word, Microsoft Excel, Microsoft Powerpoint, Microsoft Exchange, Microsoft Outlook
    \end{skills}


    \subsection{Experience}\label{subsec:experience}

    \subsubsection{Duddley's Draw}
    \hfill Cook --- \emph{August 2018 - March 2019} --- Current

    \begin{itemize}
        \tightlist{}
        \item
        Prepared a variety of delicous food-stuffs
        \item
        Worked quickly, under pressure.
    \end{itemize}


    \subsubsection{Chick-fil-a}
    \hfill Cashier and Cook --- \emph{April 2015 - December 2018 (seasonal since December 2016)} --- Left for College

    \begin{itemize}
        \tightlist{}
        \item
        Acted as a cheerful and helpful cashier on the front counter, taking orders through the drive through monitor, taking orders with iPads on the drive thru, and taking payments and delivering food at the window of the drive thru.
        \item
        Worked in fast-paced workspace to deliver fresh and delicious food within two minutes of ordering.
        \item
        Quickly confirmed order and requested specialty items to be made on time, especially during rush hours.
        \item
        Worked in kitchen, keeping frequent items stocked and quickly making specialty items to order, with attention to detail.
        \item
        Kept entire store topped up and stocked up to enable the rest of the team to work at top speed.
        \item
        Served customers in the dining area, keeping the dining area clean, refilling drinks, and making sure that every visit for every vistor is a wonderful experience.
    \end{itemize}

    \subsubsection{Forest Glen Springs Camp}
    \hfill Program Staff --- \emph{May 2017 - September 2017} --- Left for College

    \begin{itemize}
        \tightlist{}
        \item
        Worked in a team promoting safety and fun on the low ropes Challenge Course.
        Belayed campers on the climbing wall and traversing bridge, transferred campers from the climbing elements to the ziplines and encouraged them to face their fears and have fun.
        \item
        Facilitated archery and marksmanship, encouraging novice marksmen and markswomen, and teaching best practices for safety, accuracy, and excitement.
        \item
        Organized the water front activities: Stand-up paddle boards, canoes, The Blob, and kayaks, with a safety and fun oriented attitude.

        Made sure that every camper followed protocol for safety when jumping onto off the 15ft ledge for The Blob, and ensured every camper safely enjoyed paddling around the spring-water lake.
    \end{itemize}

    \subsubsection{Camp Wilderness Ridge}
    \hfill Camp Counselor --- \emph{4 weeks of July 2017} --- Left for College

    \begin{itemize}
        \tightlist{}
        \item
        Organized games and team building exercises to grow relationships, teach the campers, and have fun.
        \item
        Led the campers through low-ropes team building exercises.
        \item
        Worked through the daily bible study and nightly talk with the campers.
        \item
        Encouraged and assisted campers in memorizing the daily bible verses.
    \end{itemize}
\end{document}